{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-24 bmvc_review.tex
Revised the introduction a bit.

In this paper, we propose a single-target tracking algorithm aiming at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. Specifically, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
$300$-$400$ fps so that it could run, at least, faster than 30 fps
when it is deployed on a low-end, embedded system.\footnote{We
  empirically found this computation useful and reasonable -- the
  computation about an 1/10th scale down of computational resources
  from a typical PC to an embedded system.}

>>>>

In this paper, we propose a single-target tracking algorithm aiming at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. Specifically, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
$300$-$400$ fps so that it could run, at least, faster than 30 fps
when it is deployed on a low-end, embedded system.\footnote{In
  general, it would be very hard to compare an Intel or AMD processor
  running on a desktop or a laptop with that, e.g., ARM, of a
  single-board, embedded system in terms of run-time performance of a
  computer vision algorithm. This is primarily because of difference
  in their architectures. But we empirically found this computation
  useful and reasonable based on specific processors, e.g., Intel's i7
  quad-core vs ARM Cortex A53 -- the computation about an 1/10th scale
  down of computational resources from a typical PC to an embedded
  system.}
